R Notebook

### 2019-10-24 src/plots for paper.Rmd
plot battles continue...

```{r permulation plot}
permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") +  scale_fill_viridis_d(direction = -1)
png("../output/maxent/paper_plots/permutation_plot.png")
print(perpl)
dev.off()
```

@@

>>>>

```{r permulation plot}
permu <- read.csv("../output/maxent/models/permutation_avg.csv")

permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") +  scale_fill_viridis_d(direction = 1) + theme_half_open(12) + 
png("../output/maxent/paper_plots/permutation_plot.png")
print(perpl)
dev.off()
```

@@

now just mak

### 2019-10-24 src/testing_file.Rmd
plot battles continue...

the ggplot experiment....

```{r}
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
ss <- raster::intersect(s, mcp)  #trim to mcp

@@

ggplot() +  ggspatial::geom_spraster_rgb(mar2d) + coord_fixed()
```

>>>>

the cowplot experiment

```{r}
library(raster)
library(rgdal)
library(ggplot2)

aea <- raster("../output/env/aea.tif") #the correct CRS
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp")
ss <- raster::intersect(s, mcp)  #trim to mcp

@@

#ratify to categorical
mar2d <- ratify(mar2d)
rat <- levels(mar2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(mar2d) <- rat
apr2d <- ratify(apr2d)
rat <- levels(apr2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(apr2d) <- rat
may2d <- ratify(may2d)
rat <- levels(may2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(may2d) <- rat
jun2d <- ratify(jun2d)
rat <- levels(jun2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(jun2d) <- rat
jul2d <- ratify(jul2d)
rat <- levels(jul2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(jul2d) <- rat
aug2d <- ratify(aug2d)
rat <- levels(aug2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(aug2d) <- rat
sep2d <- ratify(sep2d)
rat <- levels(sep2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(sep2d) <- rat
oct2d <- ratify(oct2d)
rat <- levels(oct2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(oct2d) <- rat
nov2d <- ratify(nov2d)
rat <- levels(nov2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(nov2d) <- rat
dec2d <- ratify(dec2d)
rat <- levels(dec2d)[[1]]
rat$suitability <- c("< 0.5", "> 0.5")
levels(dec2d) <- rat

now the histograms

```{r}
mar <- read.csv("../output/maxent/paper_plots/prob_by_depth/mar_dis_prob_cells.csv", header = TRUE)
mar <- mar[!(mar$Depth =="1151.99" | mar$Depth =="1265.86" | mar$Depth =="1387.38"), ]
mar$Probability <- gsub(">0.9", "0.9 - 1", mar$Probability)
mar$Depth <- as.factor(mar$Depth)
flevelsmar <- levels(mar$Depth)
flevelsmar <- rev(flevelsmar)

apr <- read.csv("../output/maxent/paper_plots/prob_by_depth/apr_dis_prob_cells.csv", header = TRUE)
apr <- apr[!(apr$Depth =="1151.99" | apr$Depth =="1265.86" | apr$Depth =="1387.38"), ]
apr$Probability <- gsub(">0.9", "0.9 - 1", apr$Probability)
apr$Depth <- as.factor(apr$Depth)
flevelsapr <- levels(apr$Depth)
flevelsapr <- rev(flevelsapr)

may <- read.csv("../output/maxent/paper_plots/prob_by_depth/may_dis_prob_cells.csv", header = TRUE)
may <- may[!(may$Depth =="1151.99" | may$Depth =="1265.86" | may$Depth =="1387.38"), ]
may$Probability <- gsub(">0.9", "0.9 - 1", may$Probability)
may$Depth <- as.factor(may$Depth)
flevelsmay <- levels(may$Depth)
flevelsmay <- rev(flevelsmay)

jun <- read.csv("../output/maxent/paper_plots/prob_by_depth/jun_dis_prob_cells.csv", header = TRUE)
jun <- jun[!(jun$Depth =="1151.99" | jun$Depth =="1265.86" | jun$Depth =="1387.38"), ]
jun$Probability <- gsub(">0.9", "0.9 - 1", jun$Probability)
jun$Depth <- as.factor(jun$Depth)
flevelsjun <- levels(jun$Depth)
flevelsjun <- rev(flevelsjun)

jul <- read.csv("../output/maxent/paper_plots/prob_by_depth/jul_dis_prob_cells.csv", header = TRUE)
jul <- jul[!(jul$Depth =="1151.99" | jul$Depth =="1265.86" | jul$Depth =="1387.38"), ]
jul$Probability <- gsub(">0.9", "0.9 - 1", jul$Probability)
jul$Depth <- as.factor(jul$Depth)
flevelsjul <- levels(jul$Depth)
flevelsjul <- rev(flevelsjul)

aug <- read.csv("../output/maxent/paper_plots/prob_by_depth/aug_dis_prob_cells.csv", header = TRUE)
aug <- aug[!(aug$Depth =="1151.99" | aug$Depth =="1265.86" | aug$Depth =="1387.38"), ]
aug$Probability <- gsub(">0.9", "0.9 - 1", aug$Probability)
aug$Depth <- as.factor(aug$Depth)
flevelsaug <- levels(aug$Depth)
flevelsaug <- rev(flevelsaug)

sep <- read.csv("../output/maxent/paper_plots/prob_by_depth/sep_dis_prob_cells.csv", header = TRUE)
sep <- sep[!(sep$Depth =="1151.99" | sep$Depth =="1265.86" | sep$Depth =="1387.38"), ]
sep$Probability <- gsub(">0.9", "0.9 - 1", sep$Probability)
sep$Depth <- as.factor(sep$Depth)
flevelssep <- levels(sep$Depth)
flevelssep <- rev(flevelssep)

oct <- read.csv("../output/maxent/paper_plots/prob_by_depth/oct_dis_prob_cells.csv", header = TRUE)
oct <- oct[!(oct$Depth =="1151.99" | oct$Depth =="1265.86" | oct$Depth =="1387.38"), ]
oct$Probability <- gsub(">0.9", "0.9 - 1", oct$Probability)
oct$Depth <- as.factor(oct$Depth)
flevelsoct <- levels(oct$Depth)
flevelsoct <- rev(flevelsoct)

nov <- read.csv("../output/maxent/paper_plots/prob_by_depth/nov_dis_prob_cells.csv", header = TRUE)
nov <- nov[!(nov$Depth =="1151.99" | nov$Depth =="1265.86" | nov$Depth =="1387.38"), ]
nov$Probability <- gsub(">0.9", "0.9 - 1", nov$Probability)
nov$Depth <- as.factor(nov$Depth)
flevelsnov <- levels(nov$Depth)
flevelsnov <- rev(flevelsnov)

dec <- read.csv("../output/maxent/paper_plots/prob_by_depth/dec_dis_prob_cells.csv", header = TRUE)
dec <- dec[!(dec$Depth =="1151.99" | dec$Depth =="1265.86" | dec$Depth =="1387.38"), ]
dec$Probability <- gsub(">0.9", "0.9 - 1", dec$Probability)
dec$Depth <- as.factor(dec$Depth)
flevelsdec <- levels(dec$Depth)
flevelsdec <- rev(flevelsdec)

pm <- ggplot(mar, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmar, breaks=flevelsmar[seq(1,length(flevelsmar), by = 2)], ) + coord_flip() + labs(title = "March") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.x = element_blank())

pa <- ggplot(apr, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsapr, breaks=flevelsapr[seq(1,length(flevelsapr), by = 2)], ) + coord_flip() + labs(title = "April") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.x = element_blank(), axis.text.y = element_blank())

pma <- ggplot(may, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsmay, breaks=flevelsmay[seq(1,length(flevelsmay), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "May") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.x = element_blank(), axis.text.y = element_blank())

pj <- ggplot(jun, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjun, breaks=flevelsjun[seq(1,length(flevelsjun), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "June") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.x = element_blank(), axis.text.y = element_blank())

pju <- ggplot(jul, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsjul, breaks=flevelsjul[seq(1,length(flevelsjul), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "July") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.x = element_blank(), axis.text.y = element_blank())

pau <- ggplot(aug, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsaug, breaks=flevelsaug[seq(1,length(flevelsaug), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "August") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none")

ps <- ggplot(sep, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelssep, breaks=flevelssep[seq(1,length(flevelssep), by = 2)]) + coord_flip() +labs(y = "% Ocean at Depth", title = "September") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.y = element_blank())

po <- ggplot(oct, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsoct, breaks=flevelsoct[seq(1,length(flevelsoct), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "October") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.y = element_blank())

pn <- ggplot(nov, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() + scale_fill_viridis(option="magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsnov, breaks=flevelsnov[seq(1,length(flevelsnov), by = 2)], ) + coord_flip() + labs(y = "% Ocean at Depth", title = "November") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.y = element_blank())

pd <- ggplot(dec, aes(Depth, p_cells, fill = Probability)) + geom_col(width = 1) + coord_flip() +  scale_fill_viridis(option = "magma", discrete = TRUE, direction = -1) + scale_x_discrete(limits = flevelsdec, breaks=flevelsdec[seq(1,length(flevelsdec), by = 2)]) + coord_flip() +labs(title = "December") + theme_half_open(12) + theme(plot.margin = margin(6, 0, 6, 0), axis.title.y = element_blank(), axis.title.x = element_blank(), legend.position = "none", axis.text.y = element_blank())

pm
pa
pma
pj
pju
pau
ps
po
pn
pd
```

merge the maps and histograms into one giant plot

```{r}
maplst <- list(mar2d, pm, apr2d, pa, may2d, pma, jun2d, pj, jul2d, pju, aug2d, pa, sep2d, ps, oct2d, po, nov2d, pn, dec2d, pd)

marmap <- levelplot(mar2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
aprmap <- levelplot(apr2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
maymap <- levelplot(may2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
junmap <- levelplot(jun2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
julmap <- levelplot(jul2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
augmap <- levelplot(aug2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
sepmap <- levelplot(sep2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
octmap <- levelplot(oct2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
novmap <- levelplot(nov2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
decmap <- levelplot(dec2d, col.regions=c('white', 'red'),  colorkey = FALSE, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))

legend <- get_legend(pd +  guides(color = guide_legend(nrow = 1)) + theme(legend.position = "bottom"))

p <- plot_grid(pm, pa, pma, pj, pju, pau, ps, po, pn, pd, ncol = 5, legend)
png("../output/maxent/paper_plots/jointtest.png", height = 1024, width = 2048) #, bg = "transparent"
p
dev.off()
```

#table for tss scores etc

```{r}
dec <- read.csv("../output/maxent/models/decavgAIC.csv", header = TRUE)
colnames(dec)

our_summary1 <- list("Training AUC" = list("min" = ~ min(dec$train_AUC),
            "max" = ~ max(dec$train_AUC),
            "mean (sd)" = ~ qwraps2::mean_sd(dec$train_AUC),
       "Displacement" =
       list("min" = ~ min(.data$disp),
            "median" = ~ median(.data$disp),
            "max" = ~ max(.data$disp),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$disp)),
       "Weight (1000 lbs)" =
       list("min" = ~ min(.data$wt),
            "max" = ~ max(.data$wt),
            "mean (sd)" = ~ qwraps2::mean_sd(.data$wt)),
       "Forward Gears" =
       list("Three" = ~ qwraps2::n_perc0(.data$gear == 3),
            "Four"  = ~ qwraps2::n_perc0(.data$gear == 4),
            "Five"  = ~ qwraps2::n_perc0(.data$gear == 5))
       )
```
